% This is a curriculum vitae built using the LaTeX package moderncv
% Copyright (c) 2020 David Oniani <onianidavid@gmail.com>
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

% Compilation requirements: LaTeX Package with XeLaTeX or XeLaTeX Template

% Settings {{{

% moderncv class declaration
% Font size options: 10pt, 11pt, and 12pt
% Font family options: sans and roman
% Paper options: a4paper, letterpaper, a5paper, legalpaper, executivepaper, and landscape.
\documentclass[a4paper,10pt,sans]{moderncv}

% Themes
\moderncvstyle{classic}  % Options: banking, casual, classic, empty, oldstyle
\moderncvcolor{blue}     % Options: blue, orange, green, red, purple, grey, black

% Packages
\usepackage[utf8]{inputenc}          % Choose character encoding, UTF-8
\usepackage[margin=0.5in]{geometry}  % Adjust margins
\usepackage[normalem]{ulem}          % Cool underline
\usepackage{fancyhdr}                % Fancy headers and footers
\usepackage{multicol}                % Multiple columns

% These are the color schemes for the themes
% These color schemes are taken from the corresponding .sty files
\definecolor{classicblack}{rgb}{0.0,0.0,0.0}      % black
\definecolor{classicblue}{rgb}{0.22,0.45,0.70}    % blue
\definecolor{classicgreen}{rgb}{0.35,0.70,0.30}   % green
\definecolor{classicorange}{rgb}{0.95,0.55,0.15}  % orange
\definecolor{classicpurple}{rgb}{0.50,0.33,0.80}  % purple
\definecolor{classicred}{rgb}{0.95,0.20,0.20}     % red

% 'moderncv' loads the package 'hyperref' by itself with its own 'hypersetup'.
% This is done from 'moderncv.cls'. Hence, no need to load hyperref again.
% Instead, load the 'hypersetup' using \AfterPreamble (or \AtBeginDocument)
% hook as shown in the code below.
\AfterPreamble{%
  % PDF information and nice-looking urls
  \hypersetup{%
    pdfauthor={David Oniani},
    pdftitle={David Oniani's Curriculum Vitae},
    pdfsubject={Curriculum Vitae},
    pdfkeywords={Curriculum Vitae},
    pdflang={English},
    colorlinks=true,
    linkcolor={classicblue},
    citecolor={classicblue},
    urlcolor={classicblue}
  }
}

% Display last updated date
% \lhead{\vspace{0.8em}
%        \color{classicblue}
%        \footnotesize{Updated: \today\ by David Oniani}}

% Sometimes latex creates unnecessarily large spaces after dots. this helps to
% avoid it. This puts single spaces at the end of sentences.
\frenchspacing

% Display page number at the bottom in the center
\cfoot{\vspace{-0.75cm}\thepage}

% Change column heading for the dates (THIS IS FOR THE ALIGNMENT)
\setlength{\hintscolumnwidth}{8em}

% Change quote width
\let\originalrecomputecvlengths\recomputecvlengths%
\renewcommand*{\recomputecvlengths}{%
\originalrecomputecvlengths%
\setlength{\quotewidth}{0.8\linewidth}}

% }}}

% Personal Data {{{

\firstname{\color{classicblue} David}
\lastname{\color{classicblue} Oniani}
% \phone[mobile]{+1~(646)~565~1224}
% \email{onianidavid@gmail.com}
\homepage{www.davidoniani.com}
\social[github][www.github.com/oniani]{www.github.com/oniani}
% \social[linkedin][www.linkedin.com/in/davidoniani]{www.linkedin.com/in/davidoniani}
\quote{Visit \url{https://www.davidoniani.com} for my papers, projects, and more!}

% }}}

% Begin the document
\begin{document}

% Title {{{

\vspace*{-0.75cm}
\makecvtitle%
\vspace*{-1cm}

% }}}

% Education {{{

\section{Education}
  \cventry{08/2017 -- 05/2021}
    {B.A. Computer Science, Mathematics, \textit{magna cum laude}}
    {\href{https://www.luther.edu}{Luther College}}
    {Decorah}
    {IA}
    {Double major in computer science and mathematics.
     Academic advisor: Dr.~Alan K. Zaring.}

  \cventry{09/2011 -- 07/2016}
    {High School Diploma, 4.0/4.0 GPA}
    {\href{https://www.linkedin.com/school/komarovi-campus-school/}{Komarovi Campus School}}
    {Tbilisi}
    {Georgia}
    {Graduated with the highest honors. Represented the school in various math and physics
     Olympiads.}

% }}}

% Work Experience {{{

\section{Work Experience}
  \cventry{04/2021 -- Present}{Research Engineer}{\href{https://www.dawnlight.com}{DawnLight}}{Palo Alto}{CA}{}
    \cvlistitem{Architected, trained, and benchmarked highly performant AI model for cough detection.}
    \cvlistitem{Developed and maintained an AI sensing inference runtime for audio and radar.}
    \cvlistitem{Trained and evaluated CNN and Depthwise CNN based deep learning models.}
    \cvlistitem{Automated a pipeline of data processing, feature engineering, and model training.}
    \cvlistitem{Ported a bounding box SSD model to PyTorch Lightning and maintained it.}
    \cvlistitem{Implemented Voice Activity Detection (VAD) system using both AI and WebRTC inference.}
    \cvlistitem{Designed and wrote wrapper APIs for interacting with annotation platforms.}
    \cvlistitem{Together with the Principal Scientist, wrote a C++ signal processing library.}
    \cvlistitem{Redesigned and improved performance of feature extractor generated using MATLAB-to-C++ transpiler.}
    \cvlistitem{Coordinated efforts with the Firmware Team for low-level systems and hardware support.}
    \cvlistitem{Continuously improved the documentation quality of the Research Engineering team docs.}

  \cventry{02/2020 -- 09/2020}{Researcher \textit{(internship)}}{\href{https://www.mayo.edu/research/centers-programs/robert-d-patricia-e-kern-center-science-health-care-delivery/about}{Mayo Clinic, Kern Center}}{Rochester}{MN}{}
    \cvlistitem{First-authored several papers that got accepted at world's major AI and biomedical informatics conferences and journals (ACM-BCB, JAMIA, etc). Publications available on \href{https://www.davidoniani.com/research}{my website}.}
    \cvlistitem{Created automated COVID-19 screening tool based on decision trees to assist nurses and physicians.}
    \cvlistitem{\href{https://github.com/oniani/covid-19-chatbot}{Built chatbot as extension of GPT-2 model by applying BERT, BioBERT, USE, and tf-idf}.}
    \cvlistitem{Utilized node2vec for generating COVID-19 network embeddings and built \href{https://www.davidoniani.com/covid-19-network/}{co-occurrence network}.}
    \cvlistitem{Wrote set of programs for extracting information from thousands of EHRs (Electronic Health Record).}
    \cvlistitem{Set up Elasticsearch and indexed millions of documents for use in NLP algorithm.}
    \cvlistitem{Drafted several papers and reports, reviewed over 15 state-of-the-art AI/NLP papers.}
    \cvlistitem{Worked directly under \href{https://www.mayo.edu/research/faculty/shen-feichen-ph-d/bio-20238745}{Dr.~Feichen Shen} and \href{https://www.mayo.edu/research/faculty/wang-yanshan-ph-d/bio-20199713}{Dr.~Yanshan Wang} in the division of \href{https://www.mayo.edu/research/faculty/liu-hongfang-ph-d/bio-00055092}{Dr.~Hongfang Liu.}}

  \cventry{08/2018 -- 01/2020}{Teaching Assistant}{\href{https://www.luther.edu/computer-science/}{Luther College}}{Decorah}{IA}{}
    \cvitemwithcomment{\footnotesize{Fall 2020}}{\href{https://www.luther.edu/catalog/curriculum/computer-science/}{Computational Models (CS 260) with Dr. Alan K. Zaring.}}{}
    \cvitemwithcomment{\footnotesize{Fall 2019}}{\href{https://www.luther.edu/catalog/curriculum/computer-science/}{Object-Oriented Programming With Java (CS 252) with Dr. Shafqat A. Shad.}}{}
    \cvitemwithcomment{\footnotesize{Fall 2018}}{\href{https://www.luther.edu/catalog/curriculum/computer-science/}{Introduction to Computer Science (CS 150) with Dr. Alan K. Zaring.}}{}
    \cvlistitem{Held help hours and assisted students with homework assignments.}
    \cvlistitem{Attended all classes and answered questions during the labs.}

  \cventry{06/2018 -- 12/2018}{Web Programmer}{\href{https://www.luther.edu/its/}{Luther College, ITS - Software Development}}{Decorah}{IA}{}
    \cvlistitem{Contributed to the brand new \href{https://norsehub.luther.edu/}{Norse Hub} web system which has successfully replaced \href{https://my.luther.edu/}{my.luther.edu}.}
    \cvlistitem{Communicated with the team, wrote reports, and attended weekly SCRUM meetings.}
    \cvlistitem{Conducted performance \& load testing using JMeter and presented the results.}
    \cvlistitem{Created a data visualization tool utilizing JavaScript DOM.}
    \cvlistitem{Migrated from the Microsoft to the Linux server and refactored the Python code.}

  \cventry{03/2017 -- 07/2017}{Co-Founder and CEO}{\href{https://www.linkedin.com/company/warblerltd/}{Warbler}}{Tbilisi}{Georgia}{}
    \cvlistitem{Spearheaded the team of young and enthusiastic software developers.}
    \cvlistitem{Processed five-year data (180k+ rows) of UNE (Unified National Exams of Georgia).}
    \cvlistitem{Designed the logo; built the pitch, presentation, and the WordPress-based website for the start-up.}
    \cvlistitem{Created a social media chatbot using Chatfuel API and set up Zoho mailing system.}

  \cventry{11/2016 -- 09/2017}{Freelance Graphic Designer}{\href{https://www.behance.net}{Behance (not affiliated)}}{}{}{}
    \cvlistitem{\href{https://www.behance.net/oniani}{Designed logos and posters for various companies in the local and the global market.}}
    \cvlistitem{Instructed and taught the basics of design to several aspiring graphic designers.}

  \cventry{10/2016 -- 06/2017}{Sales Representative and Marketing Coordinator}{\href{https://www.insta.ge}{Insta LLC}}{Tbilisi}{Georgia}{}
    \cvlistitem{Partook in the complete rebuild and redesign of sales and marketing departments.}
    \cvlistitem{Contributed to the CRM, was responsible for data gathering, filtering, and entry.}
    \cvlistitem{Managed social media, responsible for targeted campaigns, copywriting, and image-editing.}
    \cvlistitem{Cold-called and contacted clients to build and maintain long-term relationships.}
    \cvlistitem{Attended a number of staff meetings and new product/partner presentations.}

% }}}

% Research Experience {{{

\section{Research Experience}
    % 08/2019 -- 12/2019
    \cvitemwithcomment{\footnotesize{Fall 2019}}{\href{https://github.com/oniani/ccl-container-types}{Directed research in programming languages with Dr.~Alan K. Zaring.}}{}
    \cvlistitem{Redesigned and made a few significant contributions to the type system.}
    \cvlistitem{Introduced the notion of container types to the language.}
    \cvlistitem{Designed relational operators for container types.}

    % 05/2019 -- 07/2019
    \cvitemwithcomment{\footnotesize{Summer 2019}}{\href{https://github.com/oniani/ira-analysis}{Collaborative research on visual persuasion with professor Richard K. Merritt.}}{}
    \cvlistitem{Trained convolutional neural networks for image recognition using PyTorch.}
    \cvlistitem{Wrote Python scripts for PDF image/text extraction and data cleanup.}
    \cvlistitem{Performed an extensive set of both statistical and textual/NLP analyses using state-of-the-art algorithms.}

    % 05/2018 -- 06/2018
    \cvitemwithcomment{\footnotesize{Summer 2018}}{\href{https://www.luther.edu/headlines/?story_id=819818}{Collaborative research on unit testing with Dr. Roman Yasinovskyy.}}{}
    \cvlistitem{Automated feedback generation for C++ programming course.}
    \cvlistitem{Redesigned and significantly improved SQL and relational algebra solution checker.}
    \cvlistitem{Designed testable practice problems for the algorithms and data structures course.}

% }}}

% Volunteer Experience {{{

\section{Volunteer Experience}
  \cvitemwithcomment{2016}{\href{https://www.transparency.ge/en}{Transparency International Georgia}}{Observed Georgian Parliamentary Elections}
  \cvitemwithcomment{2016}{\href{https://www.khanacademy.org/}{Khan Academy}}{Subtitled Georgian and Russian videos}

% }}}

% Activities and Memberships {{{

\section{Activities and Memberships}
  \cvitem{2020 - Present}{Member, Pi Mu Epsilon (Math Honor Society)}
  \cvitem{2017 - 2021}{Member, Association for Computing Machinery (ACM)}

% }}}

% Natural Language Proficiency {{{

\section{Natural Language Proficiency}
\hspace*{\fill}
\begin{minipage}{\maincolumnwidth}
  \begin{multicols}{3}
    \begin{itemize}
      \item English, Native
      \item Georgian, Native
    \end{itemize}
    \columnbreak%
    \begin{itemize}
      \item Russian, Native
      \item Japanese, Elementary
    \end{itemize}
    \columnbreak%
    \begin{itemize}
      \item Mingrelian, Native
    \end{itemize}
  \end{multicols}
\end{minipage}

% }}}

% Technical Skills {{{

\section{Technical Skills}
    \cvitem{Languages:}
        {\textbf{Advanced}: Python, Rust, Shellscript (POSIX-compliant).\newline
         \textbf{Proficient}: Haskell, Lua, C/C++, R, SQL, Java, Javascript, Zsh, HTML, CSS.\newline
         \textbf{Acquainted}: TypeScript, Prolog, Standard ML, Scheme, VBA.}
    \cvitem{Tools and Libraries:}
        {Linux, macOs, kitty, Neovim, RStudio, JupyterLab, numpy, scipy, PyTorch, TensorFlow,
         scikit-learn, pandas, polaris, OpenCL, OpenCV, SQLite, Flask, Zola, Git, GitHub,
         GitHub Actions.}
    \cvitem{Other Skills:}
        {\LaTeX, Markdown, Technical Writing.}

% }}}

% Publications {{{

\section{Publications}
  \cvitem{2021}{\href{https://spj.sciencemag.org/journals/hds/aip/9759016/}{Social and Behavioral Determinants of Health in the Era of Artificial Intelligence with Electronic Health Records: A Scoping Review} (accepted at \href{https://spj.sciencemag.org/journals/hds/}{HDS})}
  \cvitem{2020}{\href{https://dl.acm.org/doi/abs/10.1145/3388440.3412413}{A Qualitative Evaluation of Language Models on Automatic Question-Answering for COVID-19} (accepted at \href{https://acm-bcb.org}{ACM-BCB}) \textbf{[First Author]}}
  \cvitem{2020}{\href{https://academic.oup.com/jamia/article/27/8/1259/5847598}{Constructing Co-occurrence Network Embeddings to Assist Association Extraction for COVID-19 and Other Coronavirus Infectious Diseases} (accepted at \href{https://academic.oup.com/jamia}{JAMIA}) \textbf{[First Author]}}
  \cvitem{2020}{\href{https://www.davidoniani.com/research/mics2020_paper.pdf}{Setting Up Python Development Environment for Use in a Small Classroom} (accepted at \href{https://www.micsymposium.org/}{MICS})}

% }}}

% Honors and Awards {{{

\section{Honors and Awards}
  \cvitem{2017 -- 2020}{Multiple Competitive Scholarships, \href{www.luther.edu}{Luther College}}
  \cvitem{2018, 2019}{Recipient of 2 Luther College Dean's Office Summer Research Awards, \href{www.luther.edu}{Luther College}}
  \cvitem{All Semesters}{Dean's List Recipient, \href{www.luther.edu}{Luther College}}
  \cvitem{2017}{Selected Start-up (\href{https://www.linkedin.com/company/unleashar/}{UnleashAR}), TOP 200, \href{http://www.wolvessummit.com/}{Wolves Summit} (Largest Startup Conference in EU).}
  \cvitem{2016}{Gold Medal for Academic Excellence, \href{http://mes.gov.ge/?lang=eng}{Ministry of Education and Science of Georgia}}
  \cvitem{2011 -- 2016}{Multiple-time Finalist, \href{https://naec.ge/}{National Mathematics Olympiad of Georgia}.}
  \cvitem{2014}{7\textsuperscript{th} Place (TOP 10) \href{https://naec.ge/}{National Mathematics Olympiad of Georgia}}
  \cvitem{2014}{IMO \& IPhO Nominee, \href{http://mes.gov.ge/?lang=eng}{Ministry of Education and Science of Georgia}}

% }}}

% End the document
\end{document}
