% Copyright 2020 David Oniani (onianidavid@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[a4paper,10pt,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}

% Character encoding
\usepackage[utf8]{inputenc}

% Adjust the page margins
\usepackage[margin=1in]{geometry}

% Language
\usepackage[english]{babel}

% Justify text
\usepackage{ragged2e}

% Classic blue color
\definecolor{classicblue}{rgb}{0.22,0.45,0.70}

% Set spacing
\linespread{1.2}

% 'moderncv' loads the package 'hyperref' by itself with its own 'hypersetup'.
% This is done from 'moderncv.cls'. Hence, no need to load hyperref again.
% Instead, load the 'hypersetup' using \AfterPreamble (or \AtBeginDocument)
% hook as shown in the code below.
\AfterPreamble{%
  \hypersetup{%
    pdfauthor={David Oniani},
    pdftitle={David Oniani's Personal Statement for SURF},
    pdfsubject={Personal Statement, Company, SURF},
    pdfkeywords={Personal Statement, Company, SURF},
    pdflang={English},
    colorlinks=true,
    linkcolor={classicblue},
    citecolor={classicblue},
    urlcolor={classicblue}
  }
}

% Personal data
\firstname{David}
\lastname{Oniani}
\phone[mobile]{+1~(646)~565~1224}
\email{onianidavid@gmail.com}
\homepage{www.davidoniani.com}

% Recipient data
\recipient{Recruiter}{Company}
\date{\today}
\opening{Dear Recruiter,}
\closing{Sincerely,}

\begin{document}

\makelettertitle%

\justify%

After speaking with Jodi Enos-Berlage, the Rochester Semester Director at
Luther College, I was encouraged to apply for your IT Intern position at Mayo
Clinic. I was particularly happy as I am coming from a family of doctors and
have a deep and sincere interest in medical fields. While reading about and
getting acquainted with Mayo's work culture, I was astonished by your emphasis
on patient service along with your international recognition. I was very
impressed with your mission statement and its focus on education and research.
The job description was also really attractive, emphasizing mentorship and
teamwork which are so essential for shaping an enjoyable and professional
environment.

A position at an organization like Mayo fits very well with my education,
experience, and the overall background. As a computer science and mathematics
double major at a liberal arts college, my education has provided me with both
a solid general knowledge as well as a profound technical depth in the fields
of interest. I appreciate teamwork, education, and diversity.

I have gained many transferable skills as an Undergraduate Researcher whom I
was for past two summers as well as a preceptor for past two fall semesters.
The research opportunities have provided me with a set of valuable skills which
can be applied to real-world problems. Being a preceptor, on the other hand,
allowed me to strengthen the relationship with students as well as improve my
leadership skills.

I have also worked at the Software Development Department of Luther College
where I learned about the Agile and Scrum framework and have made significant
contributions to the college's websites, web platforms, and servers.

Starting coming February, I will be working as a Health Care Delivery Research
Intern at Company's Kern Center. I will be working alongside Dr.~Wang and
Dr.~Shen on natural language processing and translational science projects in
order to facilitate secondary use of EHRs for clinical and translational
science research and health care delivery improvement through artificial
intelligence, informatics, and data science approaches.

I would appreciate the opportunity to further discuss how my strengths, skills,
and knowledge would benefit Company. Thank you for your time and consideration.
I look forward to hearing from you soon.

The description of the internship has given me a sense that the position is a
great match for my interests!

See my \href{https://www.davidoniani.com}{website} for my full CV, research
papers, projects, reports, and more!

\makeletterclosing%

\end{document}
