% Copyright 2020 David Oniani (onianidavid@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[a4paper,12pt,sans]{moderncv}
\moderncvstyle{classic}
\moderncvcolor{blue}

% Character encoding
\usepackage[utf8]{inputenc}

% Adjust the page margins
\usepackage[margin=1in]{geometry}

% Language
\usepackage[english]{babel}

% Justify text
\usepackage{ragged2e}

% Classic blue color
\definecolor{classicblue}{rgb}{0.22,0.45,0.70}

% Set spacing
\linespread{1.2}

% 'moderncv' loads the package 'hyperref' by itself with its own 'hypersetup'.
% This is done from 'moderncv.cls'. Hence, no need to load hyperref again.
% Instead, load the 'hypersetup' using \AfterPreamble (or \AtBeginDocument)
% hook as shown in the code below.
\AfterPreamble{%
  \hypersetup{%
    pdfauthor={David Oniani},
    pdftitle={David Oniani's Personal Statement},
    pdfsubject={Personal Statement, Mayo Clinic},
    pdfkeywords={Personal Statement, Mayo Clinic},
    pdflang={English},
    colorlinks=true,
    linkcolor={classicblue},
    citecolor={classicblue},
    urlcolor={classicblue}
  }
}

% Personal data
\firstname{David}
\lastname{Oniani}
\phone[mobile]{+1~(646)~565~1224}
\email{onianidavid@gmail.com}
\homepage{www.davidoniani.com}

% Recipient data
\recipient{PROGRAM Recruiter}{Company}
\date{January 11, 2020}
\opening{Dear Recruiter,}
\closing{Sincerely,}

\begin{document}

\makelettertitle%

\justify%

My career aspiration is to become an R\&D-type industry researcher. My research
interests include artificial intelligence, programming languages, and virtual
reality. I have realized that all of these subfields of computer science are
deeply linked to medical fields and can be used to solve a number of problems
in these areas.

My motivation for pursuing research related to artificial intelligence stems
from my recent summer research with Prof.~Merritt where we have explored the
2016 influence campaign launched and executed by Russian IRA (so-called
Internet Research Agency). We have utilized a number of data mining, data
analysis, and machine learning techniques in order to both analyze the
persuasive strategies utilized in this campaign as well as to make future
predictions based on the data that we obtained by scraping the PDF files made
publicly available by House Intelligence Committee. Besides, a number of binary
image classifiers were trained in order to classify images based on the type of
discord it spreads (whether it is race-based, religion-based, etc).  This
research experience showed me the diverse uses of AI and made me think about
its ethics as our work was revolving around the topics that are so sensitive to
people. Coming from a family of neurosurgeons, pharmacists, and doctors, the
emergence of AI made me wonder about its applications in medical domains.
Ultimately, I have applied to and been accepted at the Kern Center for the
Science of Health Care Delivery and starting coming spring, I will be working
alongside Dr.~Wang and Dr.~Shen on natural language processing and
translational science projects in order to facilitate secondary use of EHRs for
clinical and translational science research and health care delivery
improvement through artificial intelligence, informatics, and data science
approaches.

My fall semester directed research with Dr.~Zaring has sparked my interest in
programming languages. I have gained experience in writing type-checking rules
and in designing and extending a programming language. The research included
both theoretical work with the mathematicological aspects of the language's
(CCL) specification and practical work with the existing processors for the
language. I have designed a number of new operators for the language's type
system as well introduced the notion of compound/container types to the
language. The important lesson I have learned during the research is that one
can come up with a language with a particular problem in mind in lieu of
forcing a language, adjusted for some other uses, to fit the problem. I aspire
to create languages and tools that can improve software quality and security
and increase programmer productivity for both medical and non-medical
scientists, researchers, and workers.

Recently, I have developed a keen interest in virtual reality and its
applications in medical fields. As a result, I have worked on a few projects
involving VR technologies using Unity, 3ds Max, Z Brush, and Substance Painter.
That said, as of now, I am largely inexperienced in the field, but am open to
any project involving medical VR technologies.

The description of the program has given me a sense that PROGRAM is a great
match for my interests!

See my \href{https://www.davidoniani.com}{website} for research papers,
projects, reports, and more!

\makeletterclosing%

\end{document}
